# Pokemon Project

My career that I hope to go into after graduating college is Game Development. This is why I am studying computer science! My favorite game is Pokemon. I have looked into Pokemon and stats before by watching YouTube videos, but I never considered that I could figure things out about the game on my own! I also really enjoy web design so I want to use my passions and hobbies to create something I would love to share.

## How my Simulator Works
A user opens up the shiny app and selects 2 pokemon they want to have battle. Then they press a battle button. Behind the scenes, after they click that button an equation is done for both pokemon to decide which one will win. There is a determined score for both pokemon we get by dividing the attack by the pokemon's against_type column for the type of pokemon it is against (eg. a water and fire pokemon, the fire pokemon will take the number from the against_water column and the water pokemon will take it's number from against_fire column) then adding the HP, defense, and speed. There scores will be compared, and the pokemon with the better score will be determined the winner. A message will output (eg "Pikachu Wins!"). I used the same function but changed the output to have the Pokemon's images output. There are alse 2 stat bars that will output depending on the pokemon chosen.

## Setup

### Reading in Packages

### Reading in the CSV

```{r}
library(readr)

pokemon <- read_csv("pokemon.csv")

library(tidyverse)
library(tibble)
library(ggpubr)
library(dplyr)
library(tidyr)
library(rvest)
```

### Inspecting Data

```{r}
head(pokemon)
ls(pokemon)
```

### Reading HTML to get Images

```{r}
pokemon_html <- read_html('https://bulbapedia.bulbagarden.net/wiki/List_of_Pok%C3%A9mon_by_National_Pok%C3%A9dex_number')
```

```{r}
pokemon_images <- pokemon_html %>% html_elements("tbody")
```

```{r}
pokemon_images <- pokemon_images %>% html_elements("tr") %>% html_elements("td") %>% html_elements("a") %>%  html_element("img") %>%
  html_attr("src")
```

```{r}
pokemon_images <- na.omit(pokemon_images)
```

### Filtering Images

I needed a certain types and this was the best way to get rid of useless PNGs
This ended up being redundant and it took forever. I found out I can just source the images in the files of the cloud.

```{r}
pokemon_images <- data.frame(pokemon_images ) %>%  filter_all(any_vars(!str_detect(., "HOME")))

pokemon_images <- data.frame(pokemon_images ) %>%  filter_all(any_vars(!str_detect(., "Alola")))

pokemon_images <- data.frame(pokemon_images ) %>%  filter_all(any_vars(!str_detect(., "Galar")))

pokemon_images <- data.frame(pokemon_images ) %>%  filter_all(any_vars(!str_detect(., "Hisui")))

pokemon_images <- data.frame(pokemon_images ) %>%  filter_all(any_vars(!str_detect(., "Paldea")))

pokemon_images <- data.frame(pokemon_images ) %>%  filter_all(any_vars(!str_detect(., "Castform-S")))

pokemon_images <- data.frame(pokemon_images ) %>%  filter_all(any_vars(!str_detect(., "West")))
pokemon_images <- data.frame(pokemon_images ) %>%  filter_all(any_vars(!str_detect(., "-Rainy"))) %>%  filter_all(any_vars(!str_detect(., "-Defense"))) %>%  filter_all(any_vars(!str_detect(., "-Speed")))

pokemon_images <- data.frame(pokemon_images ) %>%  filter_all(any_vars(!str_detect(., "-Sandy")))
pokemon_images <- data.frame(pokemon_images ) %>%  filter_all(any_vars(!str_detect(., "-Trash")))

pokemon_images <- data.frame(pokemon_images ) %>%  filter_all(any_vars(!str_detect(., "-Sunshine")))

pokemon_images <- data.frame(pokemon_images ) %>%  filter_all(any_vars(!str_detect(., "-Heat"))) %>%  filter_all(any_vars(!str_detect(., "-Wash"))) %>%  filter_all(any_vars(!str_detect(., "-Frost"))) %>% filter_all(any_vars(!str_detect(., "-Fan"))) %>%  filter_all(any_vars(!str_detect(., "-Mow")))

pokemon_images <- data.frame(pokemon_images ) %>% filter_all(any_vars(!str_detect(., "-Origin"))) %>% filter_all(any_vars(!str_detect(., "-Sky"))) %>% filter_all(any_vars(!str_detect(.,"-Blue"))) %>% filter_all(any_vars(!str_detect(., "-Red"))) %>% filter_all(any_vars(!str_detect(., "-Zen"))) %>% filter_all(any_vars(!str_detect(., "-Summer"))) %>% filter_all(any_vars(!str_detect(., "-Autumn"))) %>% filter_all(any_vars(!str_detect(., "-Winter"))) %>% filter_all(any_vars(!str_detect(., "-Therian"))) %>% filter_all(any_vars(!str_detect(., "-Black"))) %>% filter_all(any_vars(!str_detect(., "-Resolute")))

pokemon_images <- data.frame(pokemon_images ) %>% filter_all(any_vars(!str_detect(., "Kyurem-White"))) %>% filter_all(any_vars(!str_detect(., "-Attack"))) %>% filter_all(any_vars(!str_detect(., "-Pirouette"))) %>% filter_all(any_vars(!str_detect(., "-Pirouette"))) %>% filter_all(any_vars(!str_detect(., "Meowstic-Female.png"))) %>% filter_all(any_vars(!str_detect(., "-10Percent"))) %>% filter_all(any_vars(!str_detect(., "-Shield"))) %>% filter_all(any_vars(!str_detect(., "-Complete"))) %>% filter_all(any_vars(!str_detect(., "-Unbound"))) %>% filter_all(any_vars(!str_detect(., "Oricorio-Pom-Pom."))) %>% filter_all(any_vars(!str_detect(., "Oricorio-Pa"))) %>% filter_all(any_vars(!str_detect(., "-Sensu"))) %>% filter_all(any_vars(!str_detect(., "c-Midnight"))) %>% filter_all(any_vars(!str_detect(., "c-Dusk"))) %>% filter_all(any_vars(!str_detect(., "-School")))

pokemon_images <- data.frame(pokemon_images ) %>%  filter_all(any_vars(!str_detect(., "-Core"))) %>% filter_all(any_vars(!str_detect(., "-Dusk_Mane"))) %>% filter_all(any_vars(!str_detect(., "-Dawn"))) %>% filter_all(any_vars(!str_detect(., "-Gulping")))  %>% filter_all(any_vars(!str_detect(., "-Gorging"))) %>% filter_all(any_vars(!str_detect(., "-Amped"))) %>% filter_all(any_vars(!str_detect(., "-Noice"))) %>% filter_all(any_vars(!str_detect(., "-Indeedee-Female"))) %>% filter_all(any_vars(!str_detect(., "-Hangry")))       
```

### Cleaning up

```{r}
pokemon_images <- pokemon_images[1:801, ]
```

```{r}
pokemon_images <- gsub("//archives", "archives", pokemon_images)
```

### Adding Images to dataset

```{r}
pokemon <- pokemon %>% mutate(pokemon_images)
```

## Fixing image file names
```{r}
# Set the working directory to the directory containing the files
setwd("pokemon_battle_sim/pokemon_images/all/")

# List all files in the directory
files <- list.files(pattern = ".jpg")

# Loop through each JPG file and rename it to PNG
for (file in files) {
  new_file <- gsub(".jpg", ".png", file)
  file.rename(file, new_file)
}

# Print a message indicating the conversion is done
print("All JPG files have been converted to PNG.")
```

## Installing packages for Shiny
```{r}
# install.packages("remotes")
# 
# # Install using the remotes package
# remotes::install_github("rstudio/shinyuieditor")

```

```{r}
# launch_editor(
#     app_loc = "app.R")
```

## Changing type names to help algorithm
```{r}
pokemon <- pokemon %>%
  mutate(type1 = if_else(type1 == "fighting", "fight", type1))
pokemon <- pokemon %>%
  mutate(type2 = if_else(type2 == "fighting", "fight", type2))
```


## Coding the Algorithm
We need to have an algorithm that decides what pokemon shows up based on it's attack and how good a pokemon is against another
```{r}
battle <- function(pokemon1, pokemon2) {
  pokemon1data <- pokemon %>% filter(name == pokemon1)
  pokemon2data <- pokemon %>% filter(name == pokemon2)

  ## Create definitions for against_column
  pokemon1_against_column <- paste0("against_", pokemon2data$type1)
  pokemon2_against_column <- paste0("against_", pokemon1data$type1)
  
  if (!is.na(pokemon2data$type2)) {
    pokemon1_against_column2 <- paste0("against_", pokemon2data$type2)
  } else {
    pokemon1_against_column2 <- "against_NA"
  }
  
  if (!is.na(pokemon1data$type2)) {
    pokemon2_against_column2 <- paste0("against_", pokemon1data$type2)
  } else {
    pokemon2_against_column2 <- "against_NA"
  }

  ## Create pokemon1 and pokemon2 scores
  ## pokemon1
  pokemon1attack <- pokemon1data$attack
  pokemon1hp <- pokemon1data$hp
  pokemon1speed <- pokemon1data$speed
  pokemon1defense <- pokemon1data$defense
  
  if (pokemon1_against_column2 == "against_NA") {
    pokemon1score <- (pokemon1attack / pokemon1data[[pokemon1_against_column]]) +
      pokemon1hp +
      pokemon1speed +
      pokemon1defense
  } else {
    pokemon1score <- (pokemon1attack / (pokemon1data[[pokemon1_against_column]] + pokemon1data[[pokemon1_against_column2]])) + 
      pokemon1hp +
      pokemon1speed +
      pokemon1defense
  }
  
  ## pokemon2
  pokemon2attack <- pokemon2data$attack
  pokemon2hp <- pokemon2data$hp
  pokemon2speed <- pokemon2data$speed
  pokemon2defense <- pokemon2data$defense
  
  if (pokemon2_against_column2 == "against_NA") {
    pokemon2score <- (pokemon2attack / pokemon2data[[pokemon2_against_column]]) + 
      pokemon2hp +
      pokemon2speed +
      pokemon2defense
  } else {
    pokemon2score <- (pokemon2attack / (pokemon2data[[pokemon2_against_column]] + pokemon2data[[pokemon2_against_column2]])) + 
      pokemon2hp +
      pokemon2speed +
      pokemon2defense
  }
  

if(pokemon2score > pokemon1score){

  return(paste(pokemon2data$name, " Wins!"))

} else if(pokemon1score > pokemon2score){

  return(paste(pokemon1data$name, " Wins!"))

} else{
  return("DRAW")
}
}
```

## Testing function // squirtle wins!
```{r}

battle('Squirtle', 'Charmander')

```

## Testing function // Venusaur wins!
```{r}

battle('Venusaur', 'Machop')

```
## Writing the function for an image to pop-up
```{r}
battlePic <- function(pokemon1, pokemon2) {
  pokemon1data <- pokemon %>% filter(name == pokemon1)
  pokemon2data <- pokemon %>% filter(name == pokemon2)

  ## Create definitions for against_column
  pokemon1_against_column <- paste0("against_", pokemon2data$type1)
  pokemon2_against_column <- paste0("against_", pokemon1data$type1)
  
  if (!is.na(pokemon2data$type2)) {
    pokemon1_against_column2 <- paste0("against_", pokemon2data$type2)
  } else {
    pokemon1_against_column2 <- "against_NA"
  }
  
  if (!is.na(pokemon1data$type2)) {
    pokemon2_against_column2 <- paste0("against_", pokemon1data$type2)
  } else {
    pokemon2_against_column2 <- "against_NA"
  }

  ## Create pokemon1 and pokemon2 scores
  ## pokemon1
  pokemon1attack <- pokemon1data$attack
  pokemon1hp <- pokemon1data$hp
  pokemon1speed <- pokemon1data$speed
  pokemon1defense <- pokemon1data$defense
  
  if (pokemon1_against_column2 == "against_NA") {
    pokemon1score <- (pokemon1attack / pokemon1data[[pokemon1_against_column]]) +
      pokemon1hp +
      pokemon1speed +
      pokemon1defense
  } else {
    pokemon1score <- (pokemon1attack / (pokemon1data[[pokemon1_against_column]] + pokemon1data[[pokemon1_against_column2]])) + 
      pokemon1hp +
      pokemon1speed +
      pokemon1defense
  }
  
  ## pokemon2
  pokemon2attack <- pokemon2data$attack
  pokemon2hp <- pokemon2data$hp
  pokemon2speed <- pokemon2data$speed
  pokemon2defense <- pokemon2data$defense
  
  if (pokemon2_against_column2 == "against_NA") {
    pokemon2score <- (pokemon2attack / pokemon2data[[pokemon2_against_column]]) + 
      pokemon2hp +
      pokemon2speed +
      pokemon2defense
  } else {
    pokemon2score <- (pokemon2attack / (pokemon2data[[pokemon2_against_column]] + pokemon2data[[pokemon2_against_column2]])) + 
      pokemon2hp +
      pokemon2speed +
      pokemon2defense
  }
  

if(pokemon2score > pokemon1score){

  return(paste0("pokemon_images/all/", tolower(pokemon2), ".png"))

} else if(pokemon1score > pokemon2score){

  return(paste0("pokemon_images/all/", tolower(pokemon1), ".png"))

} else{
  return('pokemon_images/all/pokeball.png')
}
}
```


## Testing my image function
```{r}
  battlePic('Venusaur', 'Machop')
```

## Stats Bar Functionality
```{r}
stats <- function(pokemon_name){
  pokemonData <- pokemon %>% filter(name == pokemon_name)
  
  ### stats data
  pokemonAttack <- pokemonData$attack
  pokemonHP <- pokemonData$hp
  pokemonDefense <- pokemonData$defense
  pokemonSpeed <- pokemonData$speed
  
  return(
    data.frame(
      "Area" = c("Attack", "Defense", "Speed", "HP"),
      "Stats" = c(pokemonAttack,
                       pokemonDefense,
                       pokemonSpeed,
                       pokemonHP)
    )
  )
}
```
